Music adaptation: Analysis

### 2023-04-29 analysis/baseline.Rmd
made some plots for my defense
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r ioi-plot, fig.width = 6}
ggboxplot(ioi_trial, "Articulation", "Mean", color = "Dynamics", add = "jitter", facet.by = "SubNr", xlab = "Articulation", ylab = "IOIs (ms)", title = "IOI")
```

@@

```{r seq-ioi, fig.width = 7, fig.height = 2}
ioi_seq <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Category, Interval)]

@@

```{r kot-plot,  echo = FALSE, fig.width = 6}
ggboxplot(kot_trial[Subcomponent1 == "Legato"], "Articulation", "Mean", color = "Dynamics", add = "jitter", facet.by = "SubNr", xlab = "Articulation", ylab = "KOT (ms)", title = "KOT (Legato)")

@@

@@

```{r seq-kot, fig.width = 7, fig.height = 2}
kot_seq <- dt_kot[, .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, Category, Interval)]

@@

```{r vel-plot, echo = FALSE, fig.width = 6}
ggboxplot(vel_trial[Subcomponent2 == "Forte"], "Dynamics", "Mean", color = "Articulation", add = "jitter", facet.by = "SubNr", xlab = "SubNr", ylab = "Velocity", title = "KV (Forte)")

@@

@@

```{r seq-vel, fig.width = 7, fig.height = 2}
vel_seq <- dt_vel[, .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, Category, RowNr)]

@@

```{r vel-diff-plot, echo = FALSE, fig.width = 6}
ggboxplot(vel_diff_trial[Subcomponent2 == "FtoP"], "Dynamics", "Mean", color = "Articulation", add = "jitter", facet.by = "SubNr", xlab = "Dynamics", ylab = "Velocity Difference", title = "KV-Diff (FtoP)")

@@

```{r seq-vel-diff, fig.width = 7, fig.height = 2}
vel_diff_seq <- dt_vel_diff[, .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Category, Interval)]

>>>>

```{r ioi-plot, fig.width = 10}
ggboxplot(ioi_trial, "Articulation", "Mean", color = "Dynamics", add = "jitter", facet.by = "SubNr", xlab = "Articulation", ylab = "IOIs (ms)", title = "IOI")
```

@@

```{r seq-ioi, fig.width = 9, fig.height = 4}
ioi_seq <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Category, Interval)]

@@

```{r kot-plot,  echo = FALSE, fig.width = 10}
ggboxplot(kot_trial[Subcomponent1 == "Legato"], "Articulation", "Mean", color = "Dynamics", add = "jitter", facet.by = "SubNr", xlab = "Articulation", ylab = "KOT (ms)", title = "KOT (Legato)")

@@

<!-- #### Bar graph for main effect (for presentation purposes) -->

```{r kot-bar-plot, include = FALSE}
ggbarplot(kot[Subcomponent1 == "Legato" & Articulation != "Baseline"], x = "Articulation", y = "Mean", add = "mean_se", ylab = "KOT (ms)", ylim = c(40, 60), size = 2) + theme(text = element_text(size = 40))

ggbarplot(kot[Subcomponent1 == "Staccato" & Articulation != "Baseline"], x = "Articulation", y = "Mean", add = "mean_se", ylab = "KOT (ms)", ylim = c(-220, -200), size = 2) + theme(text = element_text(size = 40))
```

@@

```{r seq-kot, fig.width = 9, fig.height = 4}
kot_seq <- dt_kot[, .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, Category, Interval)]

@@

```{r vel-plot, echo = FALSE, fig.width = 10}
ggboxplot(vel_trial[Subcomponent2 == "Forte"], "Dynamics", "Mean", color = "Articulation", add = "jitter", facet.by = "SubNr", xlab = "SubNr", ylab = "Velocity", title = "KV (Forte)")

@@

<!-- #### Bar graph for main effect (for presentation purposes) -->

```{r vel-bar-plot, include = FALSE}
ggbarplot(vel[Subcomponent2 == "Forte" & Dynamics != "Baseline"], x = "Dynamics", y = "Mean", add = "mean_se", ylab = "KV (0-127)", ylim = c(75, 85), size = 2) + theme(text = element_text(size = 40)) + scale_y_continuous(breaks=seq(75, 85, 5))

ggbarplot(vel[Subcomponent2 == "Piano" & Dynamics != "Baseline"], x = "Dynamics", y = "Mean", add = "mean_se", ylab = "KV (0-127)", ylim = c(55, 65), size = 2) + theme(text = element_text(size = 40)) + scale_y_continuous(breaks=seq(55, 65, 5))

ggbarplot(vel[Subcomponent2 == "Piano" & Articulation != "Baseline"], x = "Articulation", y = "Mean", add = "mean_se", ylab = "KV (0-127)", ylim = c(55, 65), size = 2) + theme(text = element_text(size = 40)) + scale_y_continuous(breaks=seq(55, 65, 5))
```

@@

```{r seq-vel, fig.width = 9, fig.height = 4}
vel_seq <- dt_vel[, .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, Category, RowNr)]

@@

```{r vel-diff-plot, echo = FALSE, fig.width = 10}
ggboxplot(vel_diff_trial[Subcomponent2 == "FtoP"], "Dynamics", "Mean", color = "Articulation", add = "jitter", facet.by = "SubNr", xlab = "Dynamics", ylab = "Velocity Difference", title = "KV-Diff (FtoP)")

@@

```{r seq-vel-diff, fig.width = 9, fig.height = 4}
vel_diff_seq <- dt_vel_diff[, .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Category, Interval)]
